### 2015-10-09 stuff/dirfields/DirFields.tex
...

%surface (manifold) -> M, S, \Omega 
\newcommand{\M}{M}
%volume element (volume measure) -> \mu, dA, d\Omega
\newcommand{\dA}{dA}
%director field (contra-vector)
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
%director field (co-vector, flat of contra-vector)
\newcommand{\pfl}{\mathbf{p}^{\flat}}
\newcommand{\qfl}{\mathbf{q}^{\flat}}
%discrete director field (co-vector, flat of contra-vector)
\newcommand{\pflh}{\mathbf{p}^{\flat}_{h}}
\newcommand{\pflhOld}{\widehat{\mathbf{p}}^{\flat}_{h}}
\newcommand{\qflh}{\mathbf{q}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\ph}{\mathbf{p}_{h}}
%discrete PD director field (co-vector, flat of contra-vector)
\newcommand{\PDpflh}{\underline{\mathbf{p}}^{\flat}_{h}}
\newcommand{\PDqflh}{\underline{\mathbf{q}}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\PDph}{\underline{\mathbf{p}}_{h}}
\newcommand{\PDqh}{\underline{\mathbf{q}}_{h}}
%discrete PD director field OLD SOLUTION (co-vector, flat of contra-vector)
\newcommand{\PDpflhOld}{\underline{\widehat{\mathbf{p}}}^{\flat}_{h}}
%discrete director field OLD SOLUTION (contra-vector)
\newcommand{\PDphOld}{\underline{\widehat{\mathbf{p}}}_{h}}
%Frank Oseen Energy (without Lagrange term for normalizing)
\newcommand{\EOS}{E_{\text{FO}}}
%Normalizing energy
\newcommand{\EN}{E_{n}}
%Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LB}{\boldsymbol{\Delta}^{\text{\tiny RR}}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCB}{\boldsymbol{\Delta}^{\text{\tiny GD}}}
%Laplace-deRham
\newcommand{\LDR}{\boldsymbol{\Delta}^{\text{\tiny dR}}}
%discrete Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LBh}{\LB_{h}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCBh}{\LCB_{h}}
%Laplace-deRham
\newcommand{\LDRh}{\LDR_{h}}
%Landau symbol
\renewcommand{\O}{\mathcal{O}}
%Vertices
\newcommand{\V}{\mathcal{V}}
%Edges
\newcommand{\E}{\mathcal{E}}
%Faces
\newcommand{\F}{\mathcal{F}}
%edge vector
\newcommand{\e}{\mathbf{e}}
%vertex vector
\renewcommand{\v}{\mathbf{v}}
%PD-Basis
\newcommand{\PDxi}{\boldsymbol{\xi}}

@@

@@

>>>>

%surface (manifold) -> M, S, \Omega 
\newcommand{\M}{M}
%volume element (volume measure) -> \mu, dA, d\Omega
\newcommand{\dA}{dA}
%director field (contra-vector)
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
%director field (co-vector, flat of contra-vector)
\newcommand{\pfl}{\mathbf{p}^{\flat}}
\newcommand{\qfl}{\mathbf{q}^{\flat}}
%discrete director field (co-vector, flat of contra-vector)
\newcommand{\pflh}{\mathbf{p}^{\flat}_{h}}
\newcommand{\pflhOld}{\widehat{\mathbf{p}}^{\flat}_{h}}
\newcommand{\qflh}{\mathbf{q}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\ph}{\mathbf{p}_{h}}
%discrete PD director field (co-vector, flat of contra-vector)
\newcommand{\PDpflh}{\underline{\mathbf{p}}^{\flat}_{h}}
\newcommand{\PDpflhInit}{\underline{\mathbf{p}}^{\flat}_{h,0}}
\newcommand{\PDqflh}{\underline{\mathbf{q}}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\PDph}{\underline{\mathbf{p}}_{h}}
\newcommand{\PDqh}{\underline{\mathbf{q}}_{h}}
%discrete PD director field OLD SOLUTION (co-vector, flat of contra-vector)
\newcommand{\PDpflhOld}{\underline{\widehat{\mathbf{p}}}^{\flat}_{h}}
%discrete director field OLD SOLUTION (contra-vector)
\newcommand{\PDphOld}{\underline{\widehat{\mathbf{p}}}_{h}}
%Frank Oseen Energy (without Lagrange term for normalizing)
\newcommand{\EOS}{E_{\text{FO}}}
%Normalizing energy
\newcommand{\EN}{E_{n}}
%Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LB}{\boldsymbol{\Delta}^{\text{\tiny RR}}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCB}{\boldsymbol{\Delta}^{\text{\tiny GD}}}
%Laplace-deRham
\newcommand{\LDR}{\boldsymbol{\Delta}^{\text{\tiny dR}}}
%discrete Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LBh}{\LB_{h}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCBh}{\LCB_{h}}
%Laplace-deRham
\newcommand{\LDRh}{\LDR_{h}}
%Landau symbol
\renewcommand{\O}{\mathcal{O}}
%Vertices
\newcommand{\V}{\mathcal{V}}
%Edges
\newcommand{\E}{\mathcal{E}}
%Faces
\newcommand{\F}{\mathcal{F}}
%edge vector
\newcommand{\e}{\mathbf{e}}
%vertex vector
\renewcommand{\v}{\mathbf{v}}
%PD-Basis
\newcommand{\PDxi}{\boldsymbol{\xi}}
%gen. basis
\newcommand{\base}{\boldsymbol{\xi}}

@@

    \begin{align} \label{eqPDNorm}

@@

\section{Experiments}

  \subsection{Nonic Surface}

    We are starting with the standard parametrization (\(  \theta\in\left[ 0,\pi \right],\, \phi\in\left[ 0,2\pi\right) \))
    \begin{align}
      X_{\mathds{S}}(\theta,\phi) &= 
                      \sin\theta\cos\phi\base^{x} +  \sin\theta\sin\phi \base^{y} + \cos\theta\base^{z}
    \end{align}
    of the unit sphere and make a displacement in the \( \base^{x} \)-direction depending on the \( z \)-position:
    \begin{align}
      X(\theta,\phi) :=  X_{\mathds{S}}(\theta,\phi) + f(\cos\theta)\base^{x}
    \end{align}
    This results also in an implicit description of this surface in standard Euclidean \( (x,y,z) \)-coordinates:
    \begin{align}\label{eqImplicitNonic}
      \varphi(x,y,z) &:= \left( x - f(z) \right)^{2} + y^{2} + z^{2} - 1 = 0
    \end{align}
    We choose for the displacement function \( f:[-1,1]\rightarrow\R \) a double well function, 
    so that the north pole (\( z=1 \)) of the initial sphere is shifting right in  \( \base^{x} \)-direction by \( C>0 \)
    and the south pole (\( z=-1 \)) by \( r\cdot C  \) with the proportion factor \( 0 < r < 1 \).
    This implies
    \begin{align}
      f_{C,r}(z) = \frac{1}{4} C z^2 \left[(z+1)^2 (4-3 z)+r (z-1)^2 (4+3 z)\right]
    \end{align}
    and the double well conditions \( f(1) = C \), \( f(-1)=rC \) and \( f'(1)=f'(0)=f'(-1)=0 \) are fulfilled.
    We call this subsequent manifold a nonic surface, because the left-hand side of the resulting implicit description
    \eqref{eqImplicitNonic} is a polynomial of degree 10.
    The reason why we don't choose \( r = 1 \) to get a less complex surface is to break the symmetry in the 
    \( x \)-\( y \)-plane, this is necessary for preventing meta stable states in the dynamic of the orientation fields.

    An simple choice for an initial condition is
    \begin{align}
      \pfl_{0} &= \frac{\exd x}{\left\|\exd x  \right\|}
    \end{align}
    because we can discretize \( \exd x \) on an edge \( e=\left[ v_{1} , v_{2} \right] \) by (stokes theorem)
    \begin{align}
      \left( \exd x \right)_{h}(e) = \left( v_{2} - v_{1} \right)\cdot\base^{x} = v_{2}^{x} - v_{1}^{x} 
    \end{align}
    independent in the parametrization of the surface.
    Hence, after normalizing, there are three defects with a positive charge on the three bulges and one defect with a negative charge on the saddle point.
    (That are the 4 positions, where the tangential space is orthogonal to \( \base^{x} \).)
    If needed, by rising the indices we get the surface gradient of the \( x \)-component
    \begin{align}
      \left( \exd x \right)^{\sharp} &= \nabla_{\M}x
                  = \left[g^{ij}_{C,r}\partial_{j}x(\theta,\phi)\right]^{i=\theta,\phi}
                  = \left( I - \frac{\nabla \varphi_{C,r}}{\left\| \nabla \varphi_{C,r} \right\|}
                        \otimes\frac{\nabla \varphi_{C,r}}{\left\| \nabla \varphi_{C,r} \right\|} \right)\base^{x}
    \end{align}
    For the normalizing procedure, it is also the Hodge dual initial solution to discretized (the rotation of the \( x \)-component).
    If the face \( f_{1}\succ e \) is right of the edge \( e \) and \( f_{2}\succ e \) located left, 
    so that \( \star e = [c(f_{1}),c(f_{2})] \) is the dual edge, than we can approximate
    \begin{align}
      \left( *\exd x \right)_{h}(e) &= -\frac{\left| e \right|}{\left| \star e \right|} \left( \exd x \right)(\star e)
                                     = -\frac{\left| e \right|}{\left| \star e \right|} \left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x} \right)
    \end{align}
    With the discrete norm \eqref{eqPDNorm} of the PD-1-form, we obtain the initial PD-1-form on \( e \in \E \) by
    \begin{align}
      \PDpflhInit(e) = \frac{
                       \begin{bmatrix}
                          v_{2}^{x} - v_{1}^{x}\\
            -\frac{\left| e \right|}{\left| \star e \right|} \left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x} \right)
                       \end{bmatrix}_{PD}
                    }{\sqrt{\frac{1}{\left| e \right|^{2}}\left(v_{2}^{x} - v_{1}^{x}  \right)^{2}
                                     +\frac{1}{\left| \star e \right|^{2}}\left( \left[c(f_{2})  \right]^{x} - \left[c(f_{1})  \right]^{x}\right)^{2} }}
    \end{align}
    See figure \ref{figNonic}.
    \begin{figure}
      \centering
      \includegraphics[width=.9\textwidth]{bilder/Nonic50p_1.png}
      \caption{Nonic Surface with shift factor \( C = 1 \) and proportion factor \( r = 0.5 \).
               The mesh is well-centered.
               Plotted is the Gauss curvature.
               The arrows show the covariant initial solution \( \p_{0} \) on some vertices.}
      \label{figNonic}
    \end{figure}

\section{Appendix}

  \subsection{Nonic Surface}
